Estimating correspondences of deformable objects "in-the-wild"

### 2015-10-30 contents/abstract.tex
Updates from ShareLaTeX

The past few years we have witnessed the development of many methodologies for constructing and fitting statistical deformable models. The construction of Statistical Deformable Models (SDMs) usually requires careful annotation of images with regards to a set of landmarks. Annotation of images with landmarks is a tedious, laborious, expensive and labor intensive procedure. Furthermore, for some deformable objects it is not possible to find and annotate with regards to a consistent set of landmarks. Nevertheless, for the majority of objects, it is possible to extract the shape by object segmentation or even by shape drawing. In this paper, we show for the first time, to the best of our knowledge, that it is possible to construct SDMs by putting object shapes in dense correspondence. Such SDMs can be build with much less efforts and can generalize so as to describe a larger battery of objects.

>>>>

The past few years we have witnessed the development of many methodologies for constructing and fitting statistical deformable models. The construction of Statistical Deformable Models (SDMs) usually requires careful annotation of images with regards to a set of landmarks. Annotation of images with landmarks is a tedious, laborious, expensive and labor intensive procedure. Furthermore, for some deformable objects, e.g. human body, it is very  difficult to find a consistent set of landmarks or for other objects it is not possible at all to guide humans in order to annotate a collection of object images with regards to a consistent set of landmarks. Nevertheless, for the majority of objects, it is possible to extract the shape by object segmentation or even by shape drawing. In this paper, we show for the first time, to the best of our knowledge, that it is possible to construct SDMs by putting object shapes in dense correspondence. Such SDMs can be build with much less efforts and can generalize so as to describe a larger battery of objects. Furthermore, we show that by sampling on the dense model a part-based SDM can be learned with its parts being in correspondence. We apply our framework for developing an SDM of human arm and legs which can be used for the segmentation of the outline of the human body, as well as to provide better and more consistent annotations for body joints.
